\documentclass[letterpaper]{article}
\usepackage{microtype}
\usepackage[oldstyle]{ETbb}
\usepackage{xcolor}
\usepackage[margin=1in]{geometry}
\usepackage[document]{ragged2e}
\usepackage{hyperref}

\newcommand{\CVAuthor}{Brian Sniffen}
\newcommand{\CVTitle}{Brian Sniffen's executive CV}
\newcommand{\CVNote}{CV compiled on {\today} for Akamai}
\newcommand{\CVWebpage}{https://www.evenmere.org/~bts}

\definecolor{dkblue}{rgb}{0.25,0.5,0.75}

\usepackage{enumitem}
\setitemize{noitemsep,topsep=0pt,parsep=0pt,partopsep=0pt}

\usepackage{oplotsymbl}

% PDF settings and properties.
\hypersetup{
pdftitle={\CVTitle},
pdfauthor={\CVAuthor},
pdfsubject={\CVWebpage},
pdfcreator={LaTeX},
pdfproducer={},
pdfkeywords={},
unicode=true,
bookmarks=true,
bookmarksopen=true,
pdfstartview=FitH,
pdfpagelayout=SinglePage,
pdfpagemode=UseOutlines,
%hidelinks,
breaklinks}

\newcommand{\mh}{\hangindent=25pt \hangafter=1 \parindent=25pt}

\newcommand{\sect}[1]{\medskip \goodbreak {{\noindent \color{dkblue} \textsf{\large #1}\par}}\mh}
\newcommand{\job}[3]{\smallskip \goodbreak {\parindent=0pt \halign to \hsize{\textsc##\hfil&, \textrm##\hfil\tabskip=0pt plus 1 fil&\tabskip=0pt\hfil\textsf##\cr\textsc{\textbf{#2}}&\emph{#3}&\textsf{#1}\cr}}\par\mh}

\newcommand{\cmm}[1]{\href{https://en.wikipedia.org/wiki/Capability_Maturity_Model}{\textsc{cmm}#1}}

\begin{document}\thispagestyle{empty}
\begin{center}
  \textrm{\Large Brian Sniffen}

  \vskip -5pt
  \centerline{\leaders\hrule\hskip 12cm}
  
  \smallskip

  \begin{tabular}{llr}
    8 Haskell St.       & 401-239-2006 (voicemail) & bts@evenmere.org \\
    Lexington, MA 02420 & 857-413-7560 (cell)      & February, 2020
  \end{tabular}  
\end{center}

\sect{Recent Employment}
\job{2018--}{Fellow}{Akamai Technologies}
Applied technical expertise to advance the mission of the company.
Most people with this title are individual contributors; I also
managed a department of 30--50 persons.  Breaking those out here:
  \job{}{Vice President, \rm System Safety \& Resilience}{Akamai Technologies}
  \begin{itemize}
  \item Cross-functional project leadership: Principal technical lead
    of the ``severe vulnerability'' process, a board-supervised,
    \textsc{ceo}-managed investment in serious technical debts across
    the company.  We significantly mitigated Twenty-five major
    vulnerabilities since 2013.  Created the program structure that
    allowed us to repeatedly achieve projects across \textsc{vp}
    domains and business units.
  \item De-risked products \& accelerated product launch: Led the
    security architecture team reviewing new products, including
    bringing that team from \cmm{1} work coordination by e-mails and a
    chat system to \cmm{3} publication of professional reviews that
    have become the go-to resource for a technical overview across the
    company.  Created the \cmm{4} ``\textsc{ez}Path'' system that
    applies Reinertsen's lean product flow ideas to bring review \&
    analysis capability into product groups---removing latency and
    putting Engineering and Product \textsc{vp}s in control of their
    own launch timing.
  \item Team building and repair: Healed a broken and burned out team.
    An extraordinarily high-functioning team in 2006 had suffered from
    scaling and personnel problems by 2010.  It moved under my
    supervision.  After two years of intense training, motivation, and
    re-organization, we had mature processes for assessments against
    \textsc{pci-dss, hipaa/hitrust, iso 27002}, Sarbanes-Oxley, and
    Fed\textsc{ramp}.  I hired a new Director of Compliance, brought
    him up to speed, promoted him to a peer, and spun off a
    high-functioning Compliance team.  Also grew and spun off the
    teams that became the Office of the \textsc{cso} and the operational
    Sensing team.
  \item Values-first leadership: Greatly exceeded norms for employee
    retention (one undesirable departure in ten years), development of
    talent, and diversity \& inclusion.  Reduced to practice a system
    for training recent-graduate engineers to the ``Architect''
    mid-career level, reducing need to compete for these scarce people
    on the open market.
  \end{itemize}

\job{}{Chief Security Architect}{Akamai Technologies}
  \begin{itemize}
  \item Industry Expert: Foresaw the future of tech and technical
    businesses that will affect Akamai, and changed that future as
    appropriate.  Engaged with standards bodies, built relationships
    with peers across industry and academy, and informed execs of
    coming risks.  Engaged with the \textsc{tls 1.3} working group,
    averting a competitor-driven standards change that would have
    obsoleted core Akamai technology.
  \item Influence: Persuaded Engineering and Product \textsc{vp}s to
    prioritize security improvements, \textbf{ensure progress on
      security initiatives}, and pay down on technical debt.  Used the
    boundaries of the mandatory incident-response \&
    severe-vulnerability processes as terrain to adjust \textsc{batna}
    of Engineering leadership and drive voluntary improvements.
  \item Safety: Overhauled a long-standing and highly successful
    incident-response program to focus on learning from incidents and
    making new mistakes---rather than showing operational excellence
    in creating the same problems for the same customers.  Brought in
    ideas from \textsc{mit} Prof. Leveson's \textsc{stamp/cast}
    analysis to emphasize \textbf{systems engineering} and blame-free,
    all-levels reviews.  Incident frequency dropped, quality of
    customer communications improved, and process maturity improved.
    Transferred first-responder duties from \emph{ad hoc} phone trees
    to a 24/7 staffed operator desk, cutting response latency from 20
    minutes to 2 minutes.
  \item Sales: \textbf{Collaborated with sales} to handle objections
    from customer security teams---both indirectly, through an
    operational ``SecSales'' team, and directly through \textsc{ebc}s
    with security-sensitive customers.  Worked with an operational
    team to seed their database of high-quality technical responses to
    objections, reducing workload on senior staff by reducing
    responses to practice and improving process.  Brought escalations
    from every-other-deal to a rare event.  Handled those escalations
    to close ``impossible'' deals.
  \end{itemize}

  \job{2012--2018}{Chief Security Architect}{Akamai Technologies}
  \job{2011--2012}{Principal Security Architect}{Akamai Technologies}
  \job{2009--2011}{Senior Security Architect}{Akamai Technologies}
  \job{2008--2009}{Security Architect}{Akamai Technologies}

\job{2003--2008}{Lead Researcher, \rm Secure Technology
  Solutions}{MITRE Corporation}
%\mh
Designed and implemented a variety of security
  tools and programs for government sponsors, managed teams of up to
  10 people on tasks of up to 4 full-time equivalents. Coordinated
  with remote contributors and sponsors while anticipating sponsor's
  future and inarticulable needs.  Principal technical reference for
  trusted computing technology (\textsc{tpm}s).  Typical projects were briefed to \textsc{ic} \textsc{gs-15}s.
  Publications are at \href{https://www.evenmere.org/~bts/#papers}{https://www.evenmere.org/$\sim$bts/\#papers}

  \job{2000--2002}{Security Engineer, \rm Systems Engineering}{Akamai Technologies}

% \newcommand{\rateHigh}{\circletfill}
% \newcommand{\rateMed}{\circletfillha}
% \newcommand{\rateFair}{\circletfillhb}
% \newcommand{\rateLow}{\circlet}

% \sect{Selected Skills \& Conversation Topics \hfill \small \color{black} \sf legend: \rateHigh superior, \rateMed current, \rateFair rusty, \rateLow nascent/lapsed}

% \newcommand\CC{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny{\textbf{++}}}}

% {\sf
% \begin{tabular}{rl}
%   comms      & \rateHigh writing, \rateMed editing, \rateHigh teaching, \rateHigh speaking \\
%   management & \rateHigh influence, \rateHigh walking around,
%                \rateHigh one on ones,\rateHigh  listening, \rateMed
%                remote \\
%   business & \rateHigh systems engineering, \rateMed process design,
%              \rateHigh risk management \\
%   & \rateMed technical compliance, \rateHigh foresight, \rateMed
%     standards bodies \\
% %  lanaguages & \rateHigh Haskell, \rateHigh Python, \rateFair OCaml, \rateFair C, \rateLow \CC{}, \rateMed Bash, \rateMed \LaTeX \\
% %  natural languages & \rateHigh American English, \rateFair Latin, \rateLow Greek (Attic, Koine), \rateLow Hebrew \\
%   \\
%   topics & \rateHigh board games, \rateMed amateur radio, \rateHigh
%            modernist cooking, \\
%          & \rateMed cognition, \rateHigh conflict, \rateHigh planetary scale computing \\
%   authors & R.~Coram, J.~Boyd, A.~Grove, N.~Leveson, V.~Rao,
%             R.~Cialdini, D.~Pink
% \end{tabular}
% }

  \sect{Patents}
\begin{itemize}
\item Appraising systems with zero knowledge proofs; US 8422683 B2, US 8750520 B2
\item Registry of modular services and a method for automatically selecting an appropriate service to provide particular logical guarantees; US 8300788 B2
\item Attestation architecture and system; US 9276905 B2
\end{itemize}


\sect{Selected Talks \& Publications}
\begin{itemize}
\item \href{https://www.youtube.com/watch?v=bAGiXimZ4kQ}{Akamai Faster
    Forward: Crypto at Scale}, invited talk at \textsc{crypto} 2016
\item
  \href{https://www.youtube.com/watch?v=LVvDwZU-1zw&list=PLYo5nh8xQFpk1w6ElQnTqX1UczahKaOhm&index=9}{TLS
    1.3: Internet Crypto For the Next Decade}, Affinity 2018
\end{itemize}

For more, see \href{https://www.evenmere.org/~bts/#papers}{https://evenmere.org/$\sim$bts/\#papers} and \href{https://www.evenmere.org/~bts/#talks}{https://evenmere.org/$\sim$bts/\#talks}.  

\sect{Education}

\job{2000}{SB, \rm Computer Science and Engineering}{Massachusetts Institute of Technology}
Plus continuing coursework on modern cryptography, mostly from Silvio
Micali.  Thesis: \emph{Trust Economies in the Free Haven Project},
which informed early decisions in the Tor privacy-protecting network
system.

\end{document}
