\input prelude
\input eplain
\input ifpdf.sty

\ifpdf
\pdfpageheight=11in
\pdfpagewidth=8.5in
\fi

\voffset=-0.4in
\vsize=9.5in

\nopagenumbers

\centerline{{\hf Brian Sniffen}}

\vskip -5pt
\centerline{\leaders\hrule\hskip 12cm}

\smallskip

%{\parindent=0pt \baselineskip=8p t
\centerline{\vbox{\hhhf {\halign{#\hfil&\qquad\qquad\hfil#\hfil&\qquad\qquad\hfil#\cr
128 Ellison Park& 401-239-2006 (voicemail)         & bts@evenmere.org      \cr
Waltham, MA, 02452 &                      857-413-7560 (cell)     & April, 2016              \cr}}}}


% \sect{Objective} \mh My next job search will be guided by good problems
% and a good set of peers to learn from.  I expect them to be problems
% labeled ``CSO,'' ``(business unit) CTO'' or similar, and to be
% looking to learn from a CEO's senior advisors.


\sect{Recent Employment}{
  \job{2008--present}{Chief Architect \& Senior Director, \rm Information
  Security}{Akamai Technologies} \mh Hired to implement ``Plan B,'' a
  vision of a research-based backstop to a traditional network-admin
  security team.  By 2010, delivered results sufficient to replace the
  traditional team with an applied research team.  We've hired for a
  long-term view and (typically) a background outside IT
  security---emphasizing fields with a strong Safety Engineering
  culture (Chem.~Eng., Aero-Astro), or an adversarial focus (e.g.,
  veterans).  In 2016, that team is responsible for:

\unorderedlist\listcompact
\li Safety: Set Akamai's incident response, train first responders,
and engage directly with crises.  We did the work in 2012 and 2013
that let Akamai survive 2014 (Heartbleed, Shellshock, etc.) without trauma.
\li Cryptography: Centralized crypto and specialized security
engineering, leading re-investment in cryptographic excellence after a
period of benign neglect.
\li Debt Reduction: Technical leadership of the ``severe
vulnerability'' process, a board-supervised, CEO-managed investment in
serious technical debts across the company.  Twelve of the top twenty
actionable debts are mitigated or better, since 2013.
\li Product \& Platform Architecture:  security architecture team
reviewing new products, including bringing that team from CMM1 work
coordination by e-mails and a chat system to CMM3 publication of
professional reviews that have become the go-to resource for a
technical overview across the company.
\li Compliance: Healing a broken and burned out team.  Company myth
says we had push-button ISO 17799 assessments in 2006, but this had
rotted by 2010.  After two years of intense training, motivation, and
re-organization, we have mature processes for assessments against
PCI-DSS, HIPAA/HITRUST, ISO 27002, Sarbanes-Oxley, and FedRAMP.  SOC2
is underway.
\endunorderedlist

  \job{2003--2008}{Lead Researcher, \rm Secure Technology
  Solutions}{MITRE Corporation}
  \mh Designed and implemented a variety of security
  tools and programs for government sponsors, managed teams of up to
  10 people on tasks of up to 4 full-time equivalents. Coordinated
  with remote contributors and sponsors while anticipating sponsor's
  future and inarticulable needs.  Principal technical reference for
  trusted computing technology (TPMs).  Publications are at {\tt http://www.evenmere.org/$\sim$bts/\#papers}

  \job{2000--2002}{Security Engineer, \rm Systems Engineering}{Akamai
  Technologies}
  % \mh Security Engineer, founded Information Security
  % department. Responsible for integrating good security practice to
  % broad product line, architecture, process. Designer of critical
  % security infrastructure. Author of corporate Information Security
  % Program. Brought Akamai onto ISO 17799 certification path. Sales
  % support for security-conscious customers.

}



%\eject

%\centerline{{\hf Brian Sniffen}}

%\vskip -5pt
%\centerline{\leaders\hrule\hskip 12cm}

%\smallskip


\def\BBB{\setbox0=\hbox{.}\raise 1\ht0\copy0\kern -\wd0\raise 3\ht0\copy0\kern-\wd0\raise 5\ht0\box0}
\def\BB {\setbox0=\hbox{.}\raise 2\ht0\copy0\kern -\wd0\raise 4\ht0\box0}
\def\B  {\setbox0=\hbox{.}\raise 3\ht0\box0}


  
\sect{Selected Skills \& Conversation Topics \hfill \jdf \color{black} legend \hskip 0.5em \BBB current, \BB rusty, \B nascent/lapsed}{ \smallskip
\centerline{\vbox{\halign{\hfil\jdf#&\hskip 0.5em\jdf#\hfil\quad&\hfil\jdf#&\hskip 0.5em\jdf#\hfil\cr
comms    & \BBB writing, \BB editing, \BB teaching, \BBB speaking \cr
management & \BBB walking around, \BBB one on ones, \BBB listening, \BB remote\cr
languages    & \omit \jdf \hskip 0.5em  \BBB Haskell, \BBB Python, \BB OCaml, \BB C, \B C++, \B Objective C, \B Scheme,               \B Java,       \B PHP,   \BB Perl,      \BBB Bash, \BBB \LaTeX \cr
natural languages & \BBB American English, \BB Latin, \B Greek (Attic, Koine), \B Hebrew & & \cr
web tech & \omit \jdf \hskip 0.5em  \BB XML,       \BB HTML,         \B CSS,                  \BB SQL,                   \BB JS,         \BB DNS,        \BB HTTP,       \BB TLS,       \B SMTP,  \B Persona\cr
tools    & \BBB git,      \BB p4,           \BBB GNU Make,                \B autotools,             \B CPSA,        \B Alloy, \BBB Emacs, \BB vi & & \cr
network  & \BBB IPv4,                 \BB IPv6,                  \BB TCP,        \BB UDP    & & \cr
\noalign{\vskip 4pt}
topics   &  \omit \jdf \hskip 0.5em \BBB board games, \BB amateur radio, \BBB modernist cooking,  \BB cognition, \BBB conflict, \BBB planetary scale computing   \cr
authors & R.~Coram, J.~Boyd, A.~Grove, N.~Leveson, V.~Rao\cr
}}}}

\sect{Patents}{
\unorderedlist\listcompact
\li Appraising systems with zero knowledge proofs; US 8422683 B2, US 8750520 B2
\li Registry of modular services and a method for automatically selecting an appropriate service to provide particular logical guarantees; US 8300788 B2
\li Attestation architecture and system; US 9276905 B2
\endunorderedlist
}

\sect{Selected Talks \& Publications}{
See {\tt https://evenmere.org/$\sim$bts/\#papers} and {\tt https://evenmere.org/$\sim$bts/\#talks}.  

% The Evolution of TLS/SSL: Improving the Foundations of Internet Security, Akamai Edge 2014, {\tt https://www.youtube.com/watch?v=eW\_A7tUuop4}

% Bypass Surgery - Akamai's Heartbleed Response Case Study, Akamai Edge 2014, {\tt https://www.youtube.com/watch?v=Ls4hb5NOOwk}

% Celebrating Bad Crypto, SOURCE Boston 2012, {\tt https://www.youtube.com/watch?v=lMWgijyioq4}

% Scanning the Ten Petabyte Cloud: FInding the Malware that Isn't There, RSA Conference 2011, {\tt https://www.youtube.com/watch?v=AD4ZAqWksjk}
}

\sect{Education}{
\job{2000}{Bachelor of Science, \rm Computer Science and Engineering}{Massachusetts Institute of Technology}
\mh Plus continuing coursework on modern cryptography, mostly from
Silvio Micali.  A thesis on {\it Trust Economies in the Free Haven Project} is
available at {\tt http://web.mit.edu/brians/www/thesis.pdf}.  
}

% \eject

% \centerline{{\hf Brian Sniffen}}

% \vskip -5pt
% \centerline{\leaders\hrule\hskip 12cm}

% \smallskip

\end

%%% Local Variables:
%%% TeX-master: t
%%% End:
